Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-25 manuscript.tex
Minor header typo fix

We used windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005) to further investigate the evolution of the temporal dynamics of social cohesion and real-world events. In this analysis, a smaller \enquote{window} of time points is used to calculate CRQA and capture more fine-grain dynamics of two time series. The window remains the same size and \enquote{slides} diagonally up the line of identity. The changes in the CRQA metrics across the windows can reveal changes in dynamics that can then be linked to external, real-world events.
\#\#\#\# Metrics
Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each respective window. These metrics can then be plotted as a time series to visualize their evolution over time. For these analyses, we decided to visualize recurrence rate and determinism.
\#\#\#\# Parameters
In addition to the CRQA parameters, two other parameters are required when conducting WCRQA. First, a window size must be decided on. The window size will determine how many observations are used in each CRQA analysis. We conducted WCRQA with a window size of 14 to investigate the dynamics over two weeks and allow for the capture of more structure and thus a more meaningful interpretation of DET. The second parameter to be chosen is a step size. Window step size is how far the window moves up the line of identity before conducting CRQA again. We chose 1 for the step size to understand how the metrics evolve from day to day. All other CRQA metrics remained the same as previously noted.
\#\#\#\# Visualization
To visualize WCRQA, the resulting metrics from each window can be plotted as a time series. This allows for visual interpretation of the pattern or fluctuation of the metrics across time. These dynamics can then be linked to other external events. See Figures \#\#-\#\# for examples.
\#\#\#\# Permutation Test
To visualize the differences in the WCRQA metrics from those obtained by chance, a permutation test was done to set upper and lower bounds for the 95th and 99th percentiles. Using a sample size of 14, one-thousand permuted time series were generated without replacement for each real time series. The upper and lower 95th and 99th percentiles were set based on the distribution of CRQA metrics from these one-thousand CRQ analyses.

>>>>

We used windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005) to further investigate the evolution of the temporal dynamics of social cohesion and real-world events. In this analysis, a smaller \enquote{window} of time points is used to calculate CRQA and capture more fine-grain dynamics of two time series. The window remains the same size and \enquote{slides} diagonally up the line of identity. The changes in the CRQA metrics across the windows can reveal changes in dynamics that can then be linked to external, real-world events.

\hypertarget{metrics-1}{%
\paragraph{Metrics}\label{metrics-1}}

Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each respective window. These metrics can then be plotted as a time series to visualize their evolution over time. For these analyses, we decided to visualize recurrence rate and determinism.

\hypertarget{parameters-1}{%
\paragraph{Parameters}\label{parameters-1}}

In addition to the CRQA parameters, two other parameters are required when conducting WCRQA. First, a window size must be decided on. The window size will determine how many observations are used in each CRQA analysis. We conducted WCRQA with a window size of 14 to investigate the dynamics over two weeks and allow for the capture of more structure and thus a more meaningful interpretation of DET. The second parameter to be chosen is a step size. Window step size is how far the window moves up the line of identity before conducting CRQA again. We chose 1 for the step size to understand how the metrics evolve from day to day. All other CRQA metrics remained the same as previously noted.

\hypertarget{visualization}{%
\paragraph{Visualization}\label{visualization}}

To visualize WCRQA, the resulting metrics from each window can be plotted as a time series. This allows for visual interpretation of the pattern or fluctuation of the metrics across time. These dynamics can then be linked to other external events. See Figures \#\#-\#\# for examples.

\hypertarget{permutation-test-1}{%
\paragraph{Permutation Test}\label{permutation-test-1}}

To visualize the differences in the WCRQA metrics from those obtained by chance, a permutation test was done to set upper and lower bounds for the 95th and 99th percentiles. Using a sample size of 14, one-thousand permuted time series were generated without replacement for each real time series. The upper and lower 95th and 99th percentiles were set based on the distribution of CRQA metrics from these one-thousand CRQ analyses.
